Stochastic Variance Reduced Policy Gradient

### 2018-01-22 svrpg.tex
Modified experiment part and added the experimental details section into appendices

We decide to use the following models:
\begin{enumerate}
\item \emph{Cart-Pole Balancing} : 4-dimensional state space: cart position x, pole angle $\theta$, the cart velocity $\dot{x}$ , and the pole velocity $\dot{\theta}$; 1-dimensional action space: the horizontal force applied to the cart body. Reward function  is defined as $r(s, a) := 10 - (1 - cos(\theta)) - 10^{-5}\norm[] a^2$. Episodes terminates when $|x|>2.4$ or $|\theta|>0.2$ or the number of time step T is major than 100.
\item \emph{Mujoco Swimmer}: 8-dimensional state space: 3 links velocities ($v_x$ and $v_y$ of center of masses) and 2 actuated joints angles. 2-dimensional action space: the two momentums applied on actuated joints.  Reward function is defined as $r(s, a) := v_x - 10^{-4}\norm[2] a^2$. Episodes terminates when the number of time step T is major than 500.
\item \emph{Mujoco Half Cheetah}: 20-dimensional state space: 9 links and 6 actuated joints angles. 6-dimensional action space: the 6 momentums applied on actuated joints.  Reward function is defined as $r(s, a) := v_x - 0.05\norm[2] a^2$. Episodes terminates when the number of time step T is major than 500.
\end{enumerate}

In all the experiments we face with GPOMDP standard algorithm. GPOMDP uses a number of trajectories per batch that is equal to the number of trajectories used in SVRPO mini-batch size.
In SVRPO we implemented two different Adam parameters: the first one for Snapshot and the second one for sub-iterations.
The stopping condition depends on the maximum number of sub-iterations and on the step size of sub-iteration: in particular we stop if the ratio of step size to number of trajectories used results smaller in sub-iteration than in snapshot.
We fixed the maximum number of trajectories that both the algorithms can use.

\begin{tabular}{ l | c  c  c }	
  & Cart-Pole & Swimmer & Half Cheetah \\
  \hline
  State space dim  & 4 & 8 & 20 \\
  Control space dim & 1 & 2 & 6 \\
  NN Hidden layers & 8 & 32x32 & 32x32 \\
  Learning rate & $10^{-2}$ & $10^{-3}$ & $10^{-3}$ \\
  Snapshot traj & 100 & 100 & 100 \\
  Sub-iter traj & 10 & 10 & 10 \\
  Max sub-iter & 50 & 20 & 20 \\
  Traj lengths& 100 & 500 & 500 \\
  Discount $(\gamma)$& 0.99 & 0.995 & 0.99 \\
  Total traj& 10000 & 10000 & 10000 \\
  \hline  
\end{tabular}

@@

>>>>

We decide to use the following models of Rllab: \emph{Cart-Pole Balancing} ,\emph{Mujoco Swimmer},\emph{Mujoco Half Cheetah}.

In all the experiments we face with GPOMDP standard algorithm. GPOMDP uses a number of trajectories per batch that is equal to the number of trajectories used in SVRPG mini-batch size.
The neural network and the learning rate are the same for GPOMDP and SVRPG.
In SVRPG we implemented two different Adam parameters: the first one for Snapshot and the second one for sub-iterations.
The stopping condition depends on the maximum number of sub-iterations and on the step size of sub-iteration: in particular we stop if the ratio of step size to number of trajectories used results smaller in sub-iteration than in snapshot.
We fixed the maximum number of trajectories that both the algorithms can use.

The neural networks is composed by one layer with 8 neurons for Cart-Pole environment and by two layers with 32x32 neurons for Swimmer and for Half Cheetah environments. In each experiment, the length of episodes is 500 steps.

@@

\section{Experimental Details}\label{app:proofs}
Environments of our experiments are:
\begin{enumerate}
	\item \emph{Cart-Pole Balancing} : 4-dimensional state space: cart position x, pole angle $\theta$, the cart velocity $\dot{x}$ , and the pole velocity $\dot{\theta}$; 1-dimensional action space: the horizontal force applied to the cart body. Reward function  is defined as $r(s, a) := 10 - (1 - cos(\theta)) - 10^{-5}\norm[] a^2$. Episodes terminates when $|x|>2.4$ or $|\theta|>0.2$ or the number of time step T is major than 100.
	\item \emph{Mujoco Swimmer}: 12-dimensional state space: 3 links velocities ($v_x$ and $v_y$ of center of masses) and 2 actuated joints angles. 2-dimensional action space: the two momentums applied on actuated joints.  Reward function is defined as $r(s, a) := v_x - 10^{-4}\norm[2] a^2$. Episodes terminates when the number of time step T is major than 500.
	\item \emph{Mujoco Half Cheetah}: 20-dimensional state space: 9 links and 6 actuated joints angles. 6-dimensional action space: the 6 momentums applied on actuated joints.  Reward function is defined as $r(s, a) := v_x - 0.05\norm[2] a^2$. Episodes terminates when the number of time step T is major than 500.
\end{enumerate}

\centering
\begin{tabular}{| l | c  c  c |}
	\hline	
	& Cart-Pole & Swimmer & Half Cheetah \\
	\hline
	State space dimension  & 4 & 8 & 20 \\
	Control space dimension & 1 & 2 & 6 \\
	NN Hidden layers & 8 & 32x32 & 32x32 \\
	Learning rate & $10^{-2}$ & $10^{-3}$ & $10^{-3}$ \\
	Snapshot trajectories & 100 & 100 & 100 \\
	Sub-iterations trajectories/GPOMDP batch & 10 & 10 & 10 \\
	Max sub-iterations & 50 & 20 & 20 \\
	Trajectories lengths& 500 & 500 & 500 \\
	Discount $(\gamma)$& 0.99 & 0.995 & 0.99 \\
	Total trajectories& 10000 & 10000 & 10000 \\
	\hline  
\end{tabular}
